### 2024-10-22 manuscript.tex
Fix typo

\begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, \ldots\\[0.4cm]
\small
$^\mathsf{1}$Department of Meteorology (MISU) and the the Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
\large \today\\[0.4cm]

>>>>

\begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, \ldots\\[0.4cm]
\small
$^\mathsf{1}$Department of Meteorology (MISU) and the Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
\large \today\\[0.4cm]
